Item Construction Rules Revisited: Learnings from Measurement of Latent Variables with Gold Standard Items

### 2025-06-13 analysis/primary_analyses.qmd
compute fit measures for table note of tbl-4

```{r}
results <- saveRDS(
  object = list(
    table1 = table1, table2 = table2, table3 = table3, table4 = table4,
    load_df_nomod = load_df
    ), 
  file = "../results/results.rds"
)
```

>>>>

```{r}
results <- saveRDS(
  object = list(
    table1 = table1, table2 = table2, table3 = table3, table4 = table4,
    load_df_nomod = load_df,
    fullmodelfit6 = fitMeasures(fit1ges6),
    fullmodelfit2 = fitMeasures(fit1ges2)
    ), 
  file = "../results/results.rds"
)
```

### 2025-06-13 manuscript.qmd
compute fit measures for table note of tbl-4

```{r}
#| label: "tbl-4"
#| tbl-cap: Latent correlations between the latent variables age, body height and body weight, reliability estimates, and differences in $r^2$ and the corresponding self-reported physical items for 6 and 2 categories
#| ft.align: left
#| apa-note: TODO.

results$table4
```
::: {.content-visible when-format="html"}
*Note.* Above the diagonal the correlations between the latent variables are shown (printed in bold typeface) and below the diagonal the correlations between the self-reported physical measures are shown. The latent correlations were taken out of latent variable models (two and six response categories) including all self-reported physical items and all latent variables with the allocated items. The models showed the following fit: scaled chi-square (six response categories): 6203.19, df = 696, p < .001, scaled CFI: .858, scaled RMSEA = .092, SRMR= 0.109; scaled chi-square (two response categories): 3440.02, df = 696, p < .001, scaled CFI: .851, scaled RMSEA =. 065, SRMR = .122. In the diagonal (grey shaded boxes) the reliability estimates Omega for the scales can be found. The differences between the correlations of the latent variables and the self-reported physical items are shown in parentheses. * p $\leq$ .05. 
:::

>>>>

```{r}
#| label: "tbl-4"
#| tbl-cap: Latent correlations between the latent variables age, body height and body weight, reliability estimates, and differences in $r^2$ and the corresponding self-reported physical items for 6 and 2 categories
#| ft.align: left
#| apa-note: !expr 'paste0("Above the diagonal the correlations between the latent variables are shown (printed in bold typeface) and below the diagonal the correlations between the self-reported physical measures are shown. The latent correlations were taken out of latent variable models (two and six response categories) including all self-reported physical items and all latent variables with the allocated items. The models showed the following fit: scaled chi-square (six response categories) = ", printnum(results$fullmodelfit6["chisq.scaled"]), ", df = ", results$fullmodelfit6["df"], ", p ", printp(results$fullmodelfit6["pvalue.scaled"]), ", scaled CFI = ",  printnum(results$fullmodelfit6["cfi.scaled"], gt1 = FALSE), ", scaled RMSEA = ", printnum(results$fullmodelfit6["rmsea.scaled"], gt1 = FALSE), ", SRMR = ", printnum(results$fullmodelfit6["srmr"], gt1 = FALSE), "; scaled chi-square (two response categories) = ", printnum(results$fullmodelfit2["chisq.scaled"]), ", df = ", results$fullmodelfit2["df"], ", p ", printp(results$fullmodelfit2["pvalue.scaled"]), ", scaled CFI = ", printnum(results$fullmodelfit2["cfi.scaled"], gt1 = FALSE), ", scaled RMSEA = ", printnum(results$fullmodelfit2["rmsea.scaled"], gt1 = FALSE), ", SRMR = ", printnum(results$fullmodelfit2["srmr"], gt1 = FALSE), ". In the diagonal (grey shaded boxes) the reliability estimates Omega for the scales can be found. The differences between the correlations of the latent variables and the self-reported physical items are shown in parentheses. * p $\\leq$ .05.")'

results$table4
```
::: {.content-visible when-format="html"}
*Note.* Above the diagonal the correlations between the latent variables are shown (printed in bold typeface) and below the diagonal the correlations between the self-reported physical measures are shown. The latent correlations were taken out of latent variable models (two and six response categories) including all self-reported physical items and all latent variables with the allocated items. The models showed the following fit: scaled chi-square (six response categories) = `r printnum(results$fullmodelfit6["chisq.scaled"])`, df = `r results$fullmodelfit6["df"]`, p `r printp(results$fullmodelfit6["pvalue.scaled"])`, scaled CFI = `r printnum(results$fullmodelfit6["cfi.scaled"], gt1 = FALSE)`, scaled RMSEA = `r printnum(results$fullmodelfit6["rmsea.scaled"], gt1 = FALSE)`, SRMR= `r printnum(results$fullmodelfit6["srmr"], gt1 = FALSE)`; scaled chi-square (two response categories) = `r printnum(results$fullmodelfit2["chisq.scaled"])`, df = `r results$fullmodelfit2["df"]`, p `r printp(results$fullmodelfit2["pvalue.scaled"])`, scaled CFI = `r printnum(results$fullmodelfit2["cfi.scaled"], gt1 = FALSE)`, scaled RMSEA = `r printnum(results$fullmodelfit2["rmsea.scaled"], gt1 = FALSE)`, SRMR = `r printnum(results$fullmodelfit2["srmr"], gt1 = FALSE)`. In the diagonal (grey shaded boxes) the reliability estimates Omega for the scales can be found. The differences between the correlations of the latent variables and the self-reported physical items are shown in parentheses. * p $\leq$ .05. 
:::
